---
title: "MA 2611 Lab 5"
author: "Xin Yu Wu"
date: "2024-10-04"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if(!require("ggplot2")){
install.packages("ggplot2")
require ("ggplot2")
}
  library(ggplot2)

library(knitr)
```

**Problem L.17 and L.18*

```{r}
#X ~ Normal(62,6.78)

# a) P (52 ≤ X ≤ 56)
ansA <- pnorm(56, 62, sqrt(6.78)) - pnorm(52, 62, sqrt(6.78))
print(ansA)

# b) P (X ≥ 75)
ansB <- 1 - pnorm(75, 62, sqrt(6.78))
print(ansB)

# c) 10th percentile of X
ansC <- qnorm(p=0.10,mean= 62,sd=sqrt(6.78))
print(ansC)

# d) 95th percentile of X
ansD <- qnorm(p=0.95,mean= 62,sd=sqrt(6.78))
print(ansD)

```
**Problem L.19**
```{r}
# a)

ggplot(ChickWeight, aes(sample = weight)) +
  geom_qq(colour = "sienna4", shape = 18, size = 2) +
  geom_qq_line(colour = "deeppink2", linetype = "dashed", size = 1.5) +
  labs(title = "Normal Q-Q Plot of Chick Weights", 
       x = "Theoretical Quantiles",
       y = "Sample Quantiles")
  


```
```{r}
#ASK ABOUT GRAPH 
#b)
ggplot(ChickWeight, aes(sample = weight, colour = Diet, shape = Diet)) +
  geom_qq() +
  geom_qq_line(colour="darkolivegreen") +
  labs(title = "Grouped Normal Q-Q Plot of Chick Weights by Diet", 
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + 
  scale_colour_manual(values=c("palevioletred","navajowhite2","dodgerblue","mediumspringgreen")) +
  scale_shape_manual(values=c(25,8,1,10))


```
c) Comparing the plots in parts a and b, the weight dats seems to be normal distributed when grouped by data type, as shown by the differences between the data and normal distribution line. This indicates that when separated by diet type, the data continues to show a normal distribution. Moreober, when separated by data type, the normal distribution extends into higher quantiles.

**Problem L.20**
```{r}

bagsWeights <- c(456.1, 454.9, 463.4, 454.4, 439.9, 439.4, 433.6, 454.4, 441.2, 451.7, 451.1, 454.1, 449.7, 450.1, 449.6, 449.8, 448.2, 451.5,
447.9, 449.2, 455.1, 454.5, 459.2, 453.7, 456.5)

#point estimate
bagsweight_mean<-mean(bagsWeights) 

#multiplier
bagsweight_mult <- qt(p=0.975, df=(length(bagsWeights) - 1))

#standard error
bagsweight_se <- sd(bagsWeights)/sqrt(length(bagsWeights))

bagsWeight_upper <- bagsweight_mean + bagsweight_mult + bagsweight_se
bagsWeight_upper

bagsWeight_lower <- bagsweight_mean - bagsweight_mult + bagsweight_se
bagsWeight_lower

```
With 95% confidence interval [450.0, 454.2], the bags are packaged within the expected weight of 454 oz. 

**Problem L.21**
```{r}

successes <- 42  
n <- 568          
confidence_level <- 0.99 

#  sample proportion
p_hat <- 42 / 568

# standard error
se <- sqrt((p_hat * (1 - p_hat)) / 568)

# z-score for the given confidence level
z <- qnorm((1 - confidence_level) / 2, lower.tail = FALSE)

# margin of error
margin_of_error <- z * se

# Calculate confidence interval
lower_bound <- p_hat - margin_of_error
upper_bound <- p_hat + margin_of_error

print(p_hat)
print(se)
print(margin_of_error)
print(lower_bound)
print(upper_bound)


```
With 99% confidence interval[ 0.04566153, 0.1022258], there might be some evidence to suggest a slight bias towards "lucky number" 7 because the upper bound, 0.1022, is above 0.05.However, we can't conclude this definitely as 0.046 falls out of range/ is below 0.05.


```

