---
title: "MA 2611 Lab 3"
author: "Xin Yu Wu"
date: "2024-09-11"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if(!require("ggplot2")){
install.packages("ggplot2")
require ("ggplot2")
}
  library(ggplot2)

?rbinom
```

**Problem L.10**

```{r}
#a)
ggplot(data = plovers, aes(x=Eggs, y=Wingspan, fill = Eggs)) +
  geom_boxplot(fill = "chocolate4", color = "mintcream") +
  labs(title=" Boxplot of Wingspan of Plovers", 
       x ="Eggs",
       y = "Wingspan")

```

#Discrete Random Variable

```{r}
#b)
ggplot(data= plovers,aes(x= Wingspan)) +
geom_histogram(binwidth= .9, alpha = 0.5, fill="plum4", colour="thistle1") +
labs(title="Histogram of Wingspans of Plovers",x="Wingspan",y="Frequency")
```

#c)

**Problem L.11**

```{r}
#a) 
coin.1000 <-sample(x=c(0,1),size=1000,replace=TRUE,prob=c(0.8,0.2))
coin.data <-data.frame(Values=table(coin),Names=as.factor(c("0","1")))

ggplot(coin.data,aes(x=Names,y=Values.Freq)) +
geom_col(fill=c("papayawhip","mistyrose"),
colour="whitesmoke") +
labs(title="Outcomes of Unfair 1000 Coin Flips",x="Outcome",y="Frequency")

```

**Problem L.11 and L.12**

```{r}
#a) 

#Exact probability using sampled data:

mean(X_bin == 5)
mean(X_bin >= 4 & X_bin < 7)


#Exact probability using binom distribution:

sum(X_bin == 5)/20000

#The probability P is 4 <= X < 7
prob4 <- sum(X_bin == 4)/20000 
prob5 <- sum(X_bin == 5)/20000
prob6 <- sum(X_bin == 6)/20000 
probCombine <- prob4 + prob5 + prob6

print(probCombine)
```

#a) The estimated probability using sampled data is: P(X=5) = 0.21685 P(4 \<= X \< 7) = 0.6079. The estimated probability using binomial distribution is: P(X=5) = 0.21685 P(4 \<= X \< 7) = 0.6079. In this case, the estimated values are the same as the exact probabilities.

```{r}
#b)
expected_val = mean(X_bin)
standard_dev = sd(X_bin)
print(expected_val)
print(standard_dev)

Exact_expected_val = 8 * 0.5
Exact_standard_deviation <- sqrt(8 * 0.5 * (1 - 0.5))
print(Exact_expected_val)
print(Exact_standard_deviation)

```

#b) The expected value for X using the randomly sampled data is 4.0042. The standard deviation for X using the randomly sampled data is 1.410738. The exact expected value for X is 4.0. The exact standard deviation for X is 1.414214. The estimated and exact values are very close, but not exact, with a hundredth decimal difference.

```{r}
#c)
X_bin <- rbinom(n = 20000, size = 8, prob = 0.5)
X.data <-data.frame(Values=table(X_bin),Names=as.factor(c("0","1","2","3", "4","5","6","7","8")))
X.data

ggplot(X.data,aes(x=Names,y=Values.Freq)) +
geom_col(fill=c("sienna","rosybrown2","cornsilk2","tomato4","darkolivegreen","plum4","steelblue","indianred","sandybrown"),
colour="black") +
labs(title="Bar Graph of X ~ Binomial(8, 0.5) Values",x="X Values",y="Counts")                   
```
